### 2021-10-03 paper/output/document/threeflags.tex
writing on three flags

%
\begin{isabellebody}%
\setisabellecontext{paper{\isadigit{4}}{\isadigit{1}}}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Novel Formalization of the Categorical Imperative%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I present a custom formalization of the categorical imperative, as inspired by 
the goals from the previous chapter.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Logical Background%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The previous attempts to model the categorical imperative in Chapter 2 partially failed due to 
lack of expressivity about the complexity of a maxim. Specifically, they treated actions as a single, 
monolithic unit of evaluation, whereas most Kantians consider the unit of evaluation for the FUL to the more
complex notion of a maxim. In this section, I will present some logical background necessarily to more fully 
capture the spirit of a maxim. I will begin by borrowing some machinery to handle ``subjects" who perform 
actions from Chapter 2.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{typedecl}\isamarkupfalse%
\ s\ %
\isamarkupcmt{s is the type for a ``subject," i.e. the subject of a sentence%
}\isanewline
\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
\ os\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}s\ {\isasymRightarrow}\ t{\isacharparenright}{\isachardoublequoteclose}\ %
\isamarkupcmt{Recall that an open sentence maps a subject to a term to model substitution.%
}\isanewline
\isanewline
\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
\ maxim\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}t\ {\isacharasterisk}\ os\ {\isacharasterisk}\ t{\isacharparenright}{\isachardoublequoteclose}\ %
\isamarkupcmt{I define a maxim as a circumstance, act, goal tuple (C, A, G), read 
as ``In circumstances C, act A for goal G." Isabelle's strict typing rules mean that the choice of the 
type of each member of this tuple is significant. A circumstance is represented as a set of worlds 
$t$ where that circumstance holds. A goal is also a term because it can be true or false at a world if it 
is realized or not. An act is an open sentence because an act itself is not the kind of thing that can 
be true or false (as in, an act is not truth-apt), but the combination of a subject performing an act 
can be true or false at a world depending on whether or not the act is indeed performed by that subject. 
For example, ``running" is not truth-apt, but ``Sara runs" is truth-apt.%
}%
\begin{isamarkuptext}%
I define a maxim as a circumstance, act, goal tuple (C, A, G), read 
as ``In circumstances C, act A for goal G." Isabelle's strict typing rules mean that the choice of the 
type of each member of this tuple is significant. A circumstance is represented as a set of worlds 
$t$ where that circumstance holds. A goal is also a term because it can be true or false at a world if it 
is realized or not. An act is an open sentence because an act itself is not the kind of thing that can 
be true or false (as in, an act is not truth-apt), but the combination of a subject performing an act 
can be true or false at a world depending on whether or not the act is indeed performed by that subject. 
For example, ``running" is not truth-apt, but ``Sara runs" is truth-apt.

@@

While Kitcher's conception of a maxim captures Kant's idea of acting for duty's own sake, I will not implement it 
because it is not necessary for putting maxims through the FUL. Indeed, Kitcher acknowledges that 
O'Neill's formulation suffices for the universalizability test, but is not the general notion of a maxim.
In order to pass the maxim through the FUL, it suffices to know the circumstance, act, and goal. The FUL
derives the motive that Kitcher bundles into the maxim, so automating the FUL does not require 
including a motive. The ``input" to the FUL is the circumstance, act, goal pair. My project takes 
this input and returns the motivation that the dutiful, moral agent would adopt. Additionally, doing
justice to the rich notion of motive requires modelling the operation of practical reason itself, 
which is outside the scope of this project. My work focuses on the universalizability test, but future work that 
models the process of practical reason may use my implementation of the FUL as a ``library." Combined 
with a logic of practical reason, an implementation of the FUL can move from evaluating a maxim to 
evaluating an agent's behavior, since that's when ``acting from duty" starts to matter.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{fun}\isamarkupfalse%
\ will\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim\ {\isasymRightarrow}\ s{\isasymRightarrow}\ \ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}A\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}will\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharequal}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
Korsgaard claims that ``to will an end, rather than just
wishing for it or wanting it, is to set yourself to be its cause" \cite{sources}. To will a maxim, then, 
is to set yourself to, in the relevant circumstances, be the cause of its goal by taking the means 
specified in the maxim. This coheres with 
Kitcher's and Korsgaard's understanding of a maxim as a principle or rule to live by. At worlds 
where the circumstances do not hold, a maxim is vacuously willed. If you decide to act on the rule ``I will 
do X in these cirumstances", then you are vacuously obeying it when the circumstances don't hold.

The above discussion implies that willing a maxim is particular to the agent, justifying my choice to 
require that a particular subject will a maxim. O'Neill argues for this interpretation when she distinguishes 
between the evaluation of a principle, which is generic, and a maxim, which she views as ``individuated only 
by referring to a person"$\footnote{p. 13}$ \cite{actingonprinciple}. I adopt the spirit of this interpretation but modify it slightly 
by representing the general maxim as a principle that anyone could adopt, and the act of willing the maxim 
as a person-particular instantiation of the maxim.

I additionally represent a subject as willing a maxim because I use the word `will' as a verb, to mean committing oneself to living by
the principle of a maxim. This coheres with Kant's Formula of Universal Law, because it tests the willing 
of a maxim to determine if it could be a universal law that everyone committed to. Formalizing this idea,
the type of a maxim that is willed is a term, allowing me
to use DDL's obligation operator on the notion of willing a maxim.

Worlds where the circumstances do not hold are not relevant for determining obligation. Recall that in 
our definition of the obligation operator, we define $O \{B|A\}$ to be true at all worlds iff ob(B)(A), or 
if the obligation function maps A to obligatory in context B (where the context is a set of worlds). This 
definition implies that worlds outside of B have no bearing on the obligatory-ness of A in context B, which 
coheres with intuitions about obligation in a context. Thus, the dyadic obligation operator 
disqualifies worlds where the context does not hold, so the vacuous truth of the will statement in 
these worlds does not matter.

Given that the will function already excludes worlds where the circumstances fail (by rendering 
the statement vacuously true at them), one may conclude that the dyadic obligation operator is now useless. 
Using the dyadic obligation operator allows me to take advantage of the power of DDL to represent the bearing 
that circumstances have on obligation. DDL has powerful axioms expressing the relationship between circumstances 
and obligation, such as the fact that obligations are monotonically increasing with respect to broader 
circumstances. Using the monadic obligation operator would require me to either operate with an empty 
notion of context or to redefine these axioms. The dyadic obligation operator lets me take advantage of the full 
power of DDL in expressing contrary-to-duty obligations. This is particularly important for Kantian ethics 
and the FUL specifically because many critiques of the FUL rely on attention to circumstances (tailoring 
objection) or lack thereof (ideal theory). This is also an innovation that my custom formalization presents 
over the prior work. By formally including the notion of a circumstance or context, I am able to represent 
these objections that Kantian scholars study. Formalizing Kantian ethics in a dyadic deontic logic 
instead of a monadic deontic logic is a key contribution of this thesis.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{fun}\isamarkupfalse%
\ effective\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}\ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}E\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}effective\ {\isacharparenleft}c{\isacharcolon}{\isacharcolon}t{\isacharcomma}\ a{\isacharcolon}{\isacharcolon}os{\isacharcomma}\ g{\isacharcolon}{\isacharcolon}t{\isacharparenright}\ s\ {\isacharequal}\ {\isacharparenleft}{\isacharparenleft}will\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ \isactrlbold {\isasymequiv}\ g{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
A maxim is effective for a subject when, if the subject wills it then the goal is achieved, and
when the subject does not act on it, the goal is not achieved.$\footnote{Thank you to Jeremy D. Zucker for helping me think through this.}$ \cite{sepcausation} 
The former direction of the implication 
is intuitive: if the act results in the goal, it was effective in causing the goal. This represents `necessary'
causality.

The latter direction represents `sufficient' causality, or the idea that, counterfactually,
if the maxim were not willed, then the goal is not achieved \cite{lewiscausality}. Note that nothing else changes about this
counterfactual world—the circumstances are identical and we neither added additional theorems nor 
specified the model any further. This represents Lewis's idea of "comparative similarity," \cite{lewiscounterfactuals} where 
a counterfactual is true if it holds at the most similar world. In our case, this is just the world 
where everything is the same except the maxim is not acted on.

Combining these ideas, this definition of effective states that a maxim is effective if the 
maxim being acted on by a subject is the necessary and sufficient cause of the goal.\footnote{Should I wave a hand at critiques of counterfactual causality?}

If the circumstances do not hold and the goal is achieved, then the maxim is vacuously effective, since 
it is vacuously willed (as described above). While this scenario is counterintuitive, it is not very 
interesting for my purposes because, when the circumstances do not hold, a maxim is not applicable. It 
doesn't really make sense to evaluate a maxim when it's not supposed to be applied. The maxim ``When on Jupiter,
read a book to one-up your nemesis" is vacuously effective because it can never be disproven.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/paper41.thy%:%
%:%24=6%:%
%:%36=8%:%
%:%37=9%:%
%:%46=11%:%
%:%58=13%:%
%:%59=14%:%
%:%60=15%:%
%:%61=16%:%
%:%62=17%:%
%:%63=18%:%
%:%65=20%:%
%:%66=20%:%
%:%67=20%:%
%:%68=20%:%
%:%69=21%:%
%:%70=21%:%
%:%71=21%:%
%:%72=21%:%
%:%73=22%:%
%:%74=23%:%
%:%75=23%:%
%:%76=23%:%
%:%77=24%:%
%:%78=25%:%
%:%79=26%:%
%:%80=27%:%
%:%81=28%:%
%:%82=29%:%
%:%83=30%:%
%:%86=32%:%
%:%87=33%:%
%:%88=34%:%
%:%89=35%:%
%:%90=36%:%
%:%91=37%:%
%:%92=38%:%
%:%93=39%:%
%:%94=40%:%
%:%95=41%:%
%:%96=42%:%
%:%97=43%:%
%:%98=44%:%
%:%99=45%:%
%:%100=46%:%
%:%101=47%:%
%:%102=48%:%
%:%103=49%:%
%:%104=50%:%
%:%105=51%:%
%:%106=52%:%
%:%107=53%:%
%:%108=54%:%
%:%109=55%:%
%:%110=56%:%
%:%111=57%:%
%:%112=58%:%
%:%113=59%:%
%:%114=60%:%
%:%115=61%:%
%:%116=62%:%
%:%117=63%:%
%:%118=64%:%
%:%119=65%:%
%:%120=66%:%
%:%121=67%:%
%:%122=68%:%
%:%123=69%:%
%:%124=70%:%
%:%125=71%:%
%:%126=72%:%
%:%127=73%:%
%:%128=74%:%
%:%129=75%:%
%:%130=76%:%
%:%131=77%:%
%:%132=78%:%
%:%133=79%:%
%:%134=80%:%
%:%135=81%:%
%:%136=82%:%
%:%137=83%:%
%:%138=84%:%
%:%139=85%:%
%:%140=86%:%
%:%141=87%:%
%:%142=88%:%
%:%143=89%:%
%:%144=90%:%
%:%145=91%:%
%:%146=92%:%
%:%147=93%:%
%:%148=94%:%
%:%149=95%:%
%:%150=96%:%
%:%151=97%:%
%:%152=98%:%
%:%153=99%:%
%:%154=100%:%
%:%155=101%:%
%:%156=102%:%
%:%157=103%:%
%:%158=104%:%
%:%159=105%:%
%:%160=106%:%
%:%161=107%:%
%:%162=108%:%
%:%163=109%:%
%:%164=110%:%
%:%165=111%:%
%:%166=112%:%
%:%167=113%:%
%:%168=114%:%
%:%169=115%:%
%:%170=116%:%
%:%171=117%:%
%:%172=118%:%
%:%173=119%:%
%:%174=120%:%
%:%175=121%:%
%:%176=122%:%
%:%177=123%:%
%:%179=125%:%
%:%180=125%:%
%:%181=126%:%
%:%183=128%:%
%:%184=129%:%
%:%185=130%:%
%:%186=131%:%
%:%187=132%:%
%:%188=133%:%
%:%189=134%:%
%:%190=135%:%
%:%191=136%:%
%:%192=137%:%
%:%193=138%:%
%:%194=139%:%
%:%195=140%:%
%:%196=141%:%
%:%197=142%:%
%:%198=143%:%
%:%199=144%:%
%:%200=145%:%
%:%201=146%:%
%:%202=147%:%
%:%203=148%:%
%:%204=149%:%
%:%205=150%:%
%:%206=151%:%
%:%207=152%:%
%:%208=153%:%
%:%209=154%:%
%:%210=155%:%
%:%211=156%:%
%:%212=157%:%
%:%213=158%:%
%:%214=159%:%
%:%215=160%:%
%:%216=161%:%
%:%217=162%:%
%:%218=163%:%
%:%219=164%:%
%:%220=165%:%
%:%221=166%:%
%:%222=167%:%
%:%223=168%:%
%:%224=169%:%
%:%226=172%:%
%:%227=172%:%
%:%228=173%:%
%:%230=175%:%
%:%231=176%:%
%:%232=177%:%
%:%233=178%:%
%:%234=179%:%
%:%235=180%:%
%:%236=181%:%
%:%237=182%:%
%:%238=183%:%
%:%239=184%:%
%:%240=185%:%
%:%241=186%:%
%:%242=187%:%
%:%243=188%:%
%:%244=189%:%
%:%245=190%:%
%:%246=191%:%
%:%247=192%:%
%:%248=193%:%
%:%249=194%:%
%:%250=195%:%

>>>>

%
\begin{isabellebody}%
\setisabellecontext{threeflags}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\begin{isamarkuptext}%
The literature on Kantian ethics is expansive and complicated. To focus my thesis on the contributions 
of automated ethics to Kantian thought, I make the following choices.

$\textbf{Choice to Formalize the FUL}$

I am only studying formalizations of Kant's first formulation of the categorical imperative,
the formula of universal law (FUL), because it is the most formal and thus the easiest to formalize and implement. 
Onora O'Neill \cite{actingonprinciple}\footnote{p. 33} explains that the formalism of the FUL allows 
for greater precision in philosophical arguments analyzing its implications and power. This precision 
is particularly useful in a computational context because any formalism necessarily makes its content 
precise. The FUL's existing precision reduces ambiguity, allowing me to remain faithful to Kant's writing and 
philosophical interpretations of it. Precision reduces the need to make choices to resolve debates 
and ambiguities. Some of these choices may be well-studied and grounded in literature, 
but some may be unique to formalizing the FUL and thus understudied. Minimizing these choices minimizes 
arbitrariness in my formalization and puts it on solid philosophical footing. Given that this thesis is a proof-of-concept, 
the formalism of the FUL is attractive because it reduces both the computational and philosophical complexity of my work.

While some criticize the FUL for its formalism and percieved ``sterility" \cite{actingonprinciple}, 
Kantian constructivists embrace it. My project is not committed to Kantian constructivism; I argue that computational
ethics is a valuable tool for any ethicist, with a focus on general Kantian ethics. Nonetheless, Kantian constructivists may find the focus on 
the FUL particularly appealing.

Though Kantians study all formulations of the categorical imperative, Kant argues in Groundwork 
that the three formulations of the categorical imperative are equivalent \cite{groundwork}. While this 
argument is disputed \cite{sepkant}, for those who believe it, the
stakes for my choice of the FUL are greatly reduced. If all formulations are equivalent, then a formalization of the FUL
lends the exact same power as a formalization of the second or third formulation of the categorical 
imperative. In fact, future work could formalize the other formulas and try to prove that they 
are identical. Kant believes that his argument for the equality of the formulas is analytical, and
if he is correct, it should be possible to recreate the argument in logic.

$\textbf{Definition of a Maxim}$

I define a maxim as a circumstance, act, goal tuple (C, A, G), read 
as ``In circumstances C, act A for goal G." Isabelle's strict typing rules mean that the choice of the 
type of each member of this tuple is significant. A circumstance is represented as a set of worlds 
$t$ where that circumstance holds. A goal is also a term because it can be true or false at a world if it 
is realized or not. An act is an open sentence because an act itself is not the kind of thing that can 
be true or false (as in, an act is not truth-apt), but the combination of a subject performing an act 
can be true or false at a world depending on whether or not the act is indeed performed by that subject. 
For example, ``running" is not truth-apt, but ``Sara runs" is truth-apt.

@@

While Kitcher's conception of a maxim captures Kant's idea of acting for duty's own sake, I will not implement it 
because it is not necessary for putting maxims through the FUL. Indeed, Kitcher acknowledges that 
O'Neill's formulation suffices for the universalizability test, but is not the general notion of a maxim.
In order to pass the maxim through the FUL, it suffices to know the circumstance, act, and goal. The FUL
derives the motive that Kitcher bundles into the maxim, so automating the FUL does not require 
including a motive. The ``input" to the FUL is the circumstance, act, goal pair. My project takes 
this input and returns the motivation that the dutiful, moral agent would adopt. Additionally, doing
justice to the rich notion of motive requires modelling the operation of practical reason itself, 
which is outside the scope of this project. My work focuses on the universalizability test, but future work that 
models the process of practical reason may use my implementation of the FUL as a ``library." Combined 
with a logic of practical reason, an implementation of the FUL can move from evaluating a maxim to 
evaluating an agent's behavior, since that's when ``acting from duty" starts to matter.

$\textbf{Practical Contradiction Interpretation}$

Kantians debate the correct interpretation of the formula of universal law because Kant, 
at times, appears to interpret the universalizability test in different ways. My project uses Korsgaard's practical contradiction 
interpretation, broadly accepted as correct within the philosophical community \cite{ebelsduggan}\footnote{p. 177}.
Below, I briefly reconstruct Korsgaard's argument for the practical contradiction interpretation. While 
she believes that the text partially supports this interpretation, her argument is philosophical and 
derives its strength from the plausibility of the practical contradiction interpretation.

Recall that the formula of universal law is “act only in accordance with that maxim through which you can at the 
same time will that it become a universal law” \cite{groundwork}\footnote{(G: 4:421)}. To determine if a maxim can be willed as a 
universal law, one must use the “universalizability test,” which requires imagining a world in which 
everyone for all of time has willed the maxim. If willing the maxim in such a world generates a contradiction, 
then the action is prohibited. There are three interpretations of what sort of contradiction is necessary: 
(1) the teleological view, prohibiting actions that conflict with some assumed teleological end when 
universalized, (2) the logical contradiction view, prohibiting maxims that are logically impossible 
when universalized, and (3) the practical contradiction view, prohibiting maxims that are self-defeating 
when universalized.

Under the logical contradiction interpretation, falsely promising to repay a loan to get some quick cash
fails the universalizability test because, in such a world, the practice of promising would die out so 
making a false promise would be impossible. Korsgaard appeals to Dietrichson \cite{dietrichson} to construct the example of 
a mother killing her children that tend to cry more than average so that she can get some 
sleep at night. Universalizing this maxim does not generate a logical contradiction, but it is clearly 
morally wrong. The problem here is that killing is a natural action, which Korsgaard distinguishes from 
a practice, like promising. Natural actions will never be logically impossible, so the logical contradiction 
view fails to prohibit them.

Under the teleological contradiction interpretation, a maxim is prohibited if it undercuts some natural 
or assigned purpose for some practice, act, or object. For example, the purpose of promising is to 
create a system of mutual trust and false promising undercuts this purpose and is thus prohibited. The problem 
with this view is that it assumes that the agent is committed, either because of their own goals or 
because of some property of a rational will, to some teleological system. Acton formulates Hegel's argument that \cite{acton},
an agent doesn't have to be committed to promising as a system of mutual trust. Korsgaard concludes that 
assigning teleological purposes to actions is difficult because ``such purposes may have
nothing to do with what the agent wants or ought rationally to want, or even with what
any human being wants." If the agent is not committed to the purpose, then will not see a contradiction 
in willing an act that violates this purpose.

This difficulty with the teleological contradiction interpretation drives Korsgaard to look for purposes
that an agent must necessarily be committed to, and she concludes that this must be the purpose of the 
maxim itself. By willing a maxim, an agent commits themselves to the goal of the maxim, and thus cannot 
rationally will a system in which this goal is undercut. This system satisfactorily handles natural actions
like those of the sleep-deprived mother: in willing the end of sleeping through the night, she is 
implicitly willing that she be alive in order to secure and enjoy her sleep. If any mother is allowed to kill
any loud child, then she cannot be secure in the possession of her life, because her own mother may have 
grown frustrated with her crying. Her willing this maxim thwarts the end that she sought to secure.

The practical contradiction interpretation not only addresses the problems with the first two 
interpretations, it also offers a much more satisfying explanation of why certain maxims are immoral. 
The problem is not the existence of a contradiction itself, but instead the fact that these maxims 
involve parasitic behavior on social conditions that the agent seeks to benefit from. The false promiser 
simultaneously wants to abuse the system of promising and benefit from it, and is thus making an exception 
of themselves. It is this kind of free-riding that the universalizability test seeks to draw out. The test
raises the same kinds of objections that the question ``What if everyone did that?" seeks to draw out.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/threeflags.thy%:%
%:%19=7%:%
%:%20=8%:%
%:%21=9%:%
%:%22=10%:%
%:%23=11%:%
%:%24=12%:%
%:%25=13%:%
%:%26=14%:%
%:%27=15%:%
%:%28=16%:%
%:%29=17%:%
%:%30=18%:%
%:%31=19%:%
%:%32=20%:%
%:%33=21%:%
%:%34=22%:%
%:%35=23%:%
%:%36=24%:%
%:%37=25%:%
%:%38=26%:%
%:%39=27%:%
%:%40=28%:%
%:%41=29%:%
%:%42=30%:%
%:%43=31%:%
%:%44=32%:%
%:%45=33%:%
%:%46=34%:%
%:%47=35%:%
%:%48=36%:%
%:%49=37%:%
%:%50=38%:%
%:%51=39%:%
%:%52=40%:%
%:%53=41%:%
%:%54=42%:%
%:%55=43%:%
%:%56=44%:%
%:%57=45%:%
%:%58=46%:%
%:%59=47%:%
%:%60=48%:%
%:%61=49%:%
%:%62=50%:%
%:%63=51%:%
%:%64=52%:%
%:%65=53%:%
%:%66=54%:%
%:%67=55%:%
%:%68=56%:%
%:%69=57%:%
%:%70=58%:%
%:%71=59%:%
%:%72=60%:%
%:%73=61%:%
%:%74=62%:%
%:%75=63%:%
%:%76=64%:%
%:%77=65%:%
%:%78=66%:%
%:%79=67%:%
%:%80=68%:%
%:%81=69%:%
%:%82=70%:%
%:%83=71%:%
%:%84=72%:%
%:%85=73%:%
%:%86=74%:%
%:%87=75%:%
%:%88=76%:%
%:%89=77%:%
%:%90=78%:%
%:%91=79%:%
%:%92=80%:%
%:%93=81%:%
%:%94=82%:%
%:%95=83%:%
%:%96=84%:%
%:%97=85%:%
%:%98=86%:%
%:%99=87%:%
%:%100=88%:%
%:%101=89%:%
%:%102=90%:%
%:%103=91%:%
%:%104=92%:%
%:%105=93%:%
%:%106=94%:%
%:%107=95%:%
%:%108=96%:%
%:%109=97%:%
%:%110=98%:%
%:%111=99%:%
%:%112=100%:%
%:%113=101%:%
%:%114=102%:%
%:%115=103%:%
%:%116=104%:%
%:%117=105%:%
%:%118=106%:%
%:%119=107%:%
%:%120=108%:%
%:%121=109%:%
%:%122=110%:%
%:%123=111%:%
%:%124=112%:%
%:%125=113%:%
%:%126=114%:%
%:%127=115%:%
%:%128=116%:%
%:%129=117%:%
%:%130=118%:%
%:%131=119%:%
%:%132=120%:%
%:%133=121%:%
%:%134=122%:%
%:%135=123%:%
%:%136=124%:%
%:%137=125%:%
%:%138=126%:%
%:%139=127%:%
%:%140=128%:%
%:%141=129%:%
%:%142=130%:%
%:%143=131%:%
%:%144=132%:%
%:%145=133%:%
%:%146=134%:%
%:%147=135%:%
%:%148=136%:%
%:%149=137%:%
%:%150=138%:%
%:%151=139%:%
%:%152=140%:%
%:%153=141%:%
%:%154=142%:%
%:%155=143%:%
%:%156=144%:%
%:%157=145%:%
%:%158=146%:%
%:%159=147%:%
%:%160=148%:%
%:%161=149%:%
%:%162=150%:%
%:%163=151%:%
%:%164=152%:%
%:%165=153%:%
%:%166=154%:%
%:%167=155%:%
%:%168=156%:%
%:%169=157%:%
%:%170=158%:%
%:%171=159%:%
%:%172=160%:%
%:%173=161%:%
%:%174=162%:%
%:%175=163%:%
%:%176=164%:%
%:%177=165%:%
%:%178=166%:%
%:%179=167%:%
%:%180=168%:%
%:%181=169%:%
%:%182=170%:%
%:%183=171%:%
%:%184=172%:%
%:%185=173%:%
%:%186=174%:%
%:%187=175%:%
%:%188=176%:%
%:%189=177%:%
%:%190=178%:%
%:%191=179%:%
%:%192=180%:%
%:%193=181%:%
%:%194=182%:%
%:%195=183%:%
%:%196=184%:%
%:%197=185%:%
%:%198=186%:%
%:%199=187%:%
